---
title: "Operating Unit Level (OU Level)"
author: Mayer Atnoine
date: "December 27,2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(fig.path = "../Figs/")
```

```{r init, warning= FALSE, message=FALSE}
library(kableExtra)
library(xtable)

```

## `r country_name`


### PEPFAR Context

* Number of Facilities, ART and Testing
* PLHIV
* ART proportion of saturation and non-saturation district

### Geographic distribution (Maps and Coverage)

### Overall Achievement (against Target)

This table shows overall achievement for `r country_name` from FY15 to FY17

```{r ou_level,warning= FALSE, message=FALSE}

knitr::kable(ou_level,"html") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                  full_width = F, position = "center",font_size = 12)

```
***

#### Overall Indicator achievement

```{r fig_ou_level ,warning= FALSE, message=FALSE}

 ou_level %>%
    filter(!(indicator %in% c("TB_STAT_POS","OVC_HIVSTAT","OVC_SERV"))) %>%
    ggplot(aes(x = reorder(indicator, fy2017Perf), y = fy2017Perf)) +
    geom_bar(stat = "identity",fill="#0072B2") +
    geom_hline(yintercept = 85)+
    geom_text(aes(x = reorder(indicator, fy2017Perf), y = fy2017Perf,
                  label=paste0(sprintf("%.0f",round(fy2017Perf,0)),"%")),size = 4, hjust =-0.05) +
    coord_flip()+
    labs(y="% of achievement", 
         x="",
         fill="",
         title="APR17 Overall Performance",
         subtitle="",
         caption="Data source:ICPI FactView SitexIM")+
    #scale_y_continuous(limits=c(0,180))+
    #scale_y_continuous(labels = percent_format())+
    guides(fill = FALSE) +
    theme(axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12), 
          panel.background = element_blank(),
          axis.line= element_line(),
          axis.title.x = element_text(size = 10),
          plot.title = element_text(size = 12) )



```



#### Cascade FY17

```{r fig_cascade ,warning= FALSE, message=FALSE}

 ou_level %>%
    filter(indicator %in% c("HTS_TST_POS","TX_NEW","TX_NET_NEW")) %>%
    select(indicator,fy2017Cum,fy2017_targets) %>%
    ggplot(aes(x = reorder(indicator,-fy2017Cum),y= fy2017Cum))+
    geom_bar(stat = "identity", width = 0.7) +
    geom_text(aes(label= comma(fy2017Cum)),size=4.5,vjust = 1.5,colour = "white") +
    geom_errorbar(aes(ymin=fy2017_targets,ymax=fy2017_targets),width=0.5, size=1.5, color="#FF7F00")+
    labs(y="", 
         x="",
         fill="",
         title="FY17 Cascade",
         subtitle="",
         caption= "Data source:ICPI FactView SitexIM")+
    theme(axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 13,face= "bold"), 
          panel.background = element_blank(),
          axis.line=element_line(),
          axis.title.x = element_text(size = 10),
          plot.title = element_text(size = 12),
          plot.subtitle = element_text(size = 12),
          axis.ticks.y = element_blank())  



```



#### TX_NEW Trend

```{r fig_tx_new_trend ,warning= FALSE, message=FALSE}

 site_im %>%
    filter(indicator == "TX_NEW") %>%
    filter(disaggregate == "Total Numerator") %>%
    filter(indicatortype == "DSD") %>% 
    filter(numeratordenom == "N") %>%
    select(indicator,fy2015q3,fy2015q4,fy2016q1,fy2016q2,fy2016q3,fy2016q4,
           fy2017q1,fy2017q2,fy2017q3,fy2017q4,fy2017_targets) %>%
    group_by(indicator) %>%
    summarise(fy2015q3 = sum(fy2015q3, na.rm = T),
              fy2015q4 = sum(fy2015q4, na.rm = T),
              fy2016q1 = sum(fy2016q1, na.rm = T),
              fy2016q2 = sum(fy2016q2, na.rm = T),
              fy2016q3 = sum(fy2016q3, na.rm = T),
              fy2016q4 = sum(fy2016q4, na.rm = T),
              fy2017q1 = sum(fy2017q1, na.rm = T),
              fy2017q2 = sum(fy2017q2, na.rm = T),
              fy2017q3 = sum(fy2017q3,na.rm = T),
              fy2017q4 = sum(fy2017q4,na.rm = T)) %>%
    gather("fiscal_year","results",2:11) %>%
    ggplot(aes(fiscal_year,results))+
    geom_bar(stat = "identity", fill = "#0072B2",width  = 0.7)+
    geom_text(aes( y = results,
                   label=paste0(sprintf("%.0f",round(results,0)))),size = 4,vjust =-1.1 )+
    labs(y="# new people enroled on ART", 
         x="",
         fill="",
         title="TX_NEW Trend from FY15 to FY17",
         subtitle="",
         caption="Data source: ICPI FactView SitexIM")+
    scale_y_continuous(breaks = seq(0,40000,10000),limits =c(0,40000),labels =comma,expand = c(0, 0))+
    expand_limits(x = 0, y = 0)+
    theme(axis.text.x = element_text(size = 10,face="bold"),
          axis.text.y = element_text(size = 13,face= "bold"), 
          panel.background = element_blank(),
          axis.line=element_line(),
          axis.title.x = element_text(size = 8),
          plot.title = element_text(size = 12),
          plot.subtitle  = element_text(size = 12))   


```



#### TX_CURR Trend

```{r fig_tx_curr_trend ,warning= FALSE, message=FALSE}

 site_im %>%
    filter(snu1 != "_Military Haiti") %>%
    filter(indicator == "TX_CURR") %>%
    filter(disaggregate == "Total Numerator") %>%
    filter(indicatortype == "DSD") %>% 
    filter(numeratordenom == "N") %>%
    select(indicator,fy2015q4,fy2016q2,fy2016q4,
           fy2017q1,fy2017q2,fy2017q3,fy2017q4) %>%
    group_by(indicator) %>%
    summarise(fy2015q4 = sum(fy2015q4, na.rm = T),
              fy2016q2 = sum(fy2016q2, na.rm = T),
              fy2016q4 = sum(fy2016q4, na.rm = T),
              fy2017q1 = sum(fy2017q1, na.rm = T),
              fy2017q2 = sum(fy2017q2, na.rm = T),
              fy2017q3 = sum(fy2017q3,na.rm = T),
              fy2017q4 = sum(fy2017q4,na.rm = T)) %>%
    gather("quarter","results",2:8) %>%
    ggplot(aes(x=factor(quarter),y=results, group =1))+
        geom_line()+
        geom_point()+
    geom_text(aes( y = results,
                   label=paste0(sprintf("%.0f",round(results,0)))),size = 4,vjust =-1.1 )+
    labs(y="# patient on ART", 
         x="",
         fill="",
         title="TX_CURR Trend from FY15 to FY17",
         subtitle="",
         caption="Data source: ICPI FactView SitexIM")+
    #scale_y_continuous(breaks = seq(0,100000,10000),limits =c(0,100000),labels =comma,expand = c(0, 0))+
    expand_limits(x = 0, y = 0)+
    theme(axis.text.x = element_text(size = 10,face="bold"),
          axis.text.y = element_text(size = 13,face= "bold"), 
          panel.background = element_blank(),
          axis.line=element_line(),
          axis.title.x = element_text(size = 8),
          plot.title = element_text(size = 12),
          plot.subtitle  = element_text(size = 12))


```



#### HTS and PMTCT_STAT yield

```{r fig_hts_yield ,warning= FALSE, message=FALSE}

 site_im %>%
    filter(snu1 != "_Military Haiti") %>%
    filter(indicator %in% c("HTS_TST","HTS_TST_POS","PMTCT_STAT","PMTCT_STAT_POS")) %>%
    filter(disaggregate == "Total Numerator") %>%
    filter(indicatortype == "DSD") %>% 
    filter(numeratordenom == "N") %>%
    select(indicator,fy2015q4,fy2016q2,fy2016q4,
           fy2017q1,fy2017q2,fy2017q3,fy2017q4) %>%
    group_by(indicator) %>%
    summarise(fy2015q4 = sum(fy2015q4, na.rm = T),
              fy2016q2 = sum(fy2016q2, na.rm = T),
              fy2016q4 = sum(fy2016q4, na.rm = T),
              fy2017q1 = sum(fy2017q1, na.rm = T),
              fy2017q2 = sum(fy2017q2, na.rm = T),
              fy2017q3 = sum(fy2017q3,na.rm = T),
              fy2017q4 = sum(fy2017q4,na.rm = T)) %>%
    gather("quarter","results",2:8) %>%
    spread(indicator,results) %>%
    mutate(HTS_YIELD = round(HTS_TST_POS/HTS_TST,3),
           PMTCT_STAT_YIELD = round(PMTCT_STAT_POS/ PMTCT_STAT,3)) %>%
    select(quarter,HTS_YIELD,PMTCT_STAT_YIELD) %>%
    gather("indicator","results",2:3) %>%
    ggplot(aes(x=factor(quarter),y=results, group =1))+
    geom_line()+
    geom_point()+
    geom_text(aes( y = results,
                   label=paste0(results*100,"%")),size = 4,vjust =-1.1 )+
    facet_wrap(~indicator)+
    labs(y="% Yield", 
         x="",
         fill="",
         title="HTS_TST Yield Trend from FY15 to FY17",
         subtitle="",
         caption="Data source: ICPI FactView SitexIM")+
   # scale_y_continuous(limits =c(0,0.05),labels = percent_format(),expand = c(0, 0))+
    expand_limits(x = 0, y = 0)+
    theme(axis.text.x = element_text(size = 10,face="bold"),
          axis.text.y = element_text(size = 13,face= "bold"), 
          panel.background = element_blank(),
          axis.line=element_line(),
          axis.title.x = element_text(size = 8),
          plot.title = element_text(size = 12),
          plot.subtitle  = element_text(size = 12))


```


### Maps Coverage and HTS Yield


#### Linkage to Treatment

```{r fig_linkage ,warning= FALSE, message=FALSE}

 site_im %>%
    filter(indicator %in% c("HTS_TST_POS","TX_NEW")) %>%
    filter(disaggregate == "Total Numerator") %>%
    filter(numeratordenom == "N") %>%
    select(indicator,fy2015apr,fy2016apr,fy2017apr) %>%
    group_by(indicator) %>%
    summarise(fy2015apr = sum(fy2015apr, na.rm = T),
              fy2016apr = sum(fy2016apr, na.rm = T),
              fy2017apr = sum(fy2017apr,na.rm = T)) %>%
    gather("year","results",2:4) %>%
    #spread(indicator,results) %>%
    #mutate(linkage =as.numeric(round(TX_NEW/HTS_TST_POS,3))) %>%
    #gather("indicator","results",2:4) %>%
    ggplot(aes(x=year,y=results,fill = indicator))+
        geom_bar(stat = "identity",position = "dodge")+
    geom_text(aes(y = results,label=comma(results)),
              position = position_dodge(width = 1.1),vjust =-1.1)+
    labs(y="# of patients", 
         x="",
         fill="",
         title="Linkage to Treatment",
         subtitle="",
         caption="Data source: ICPI FactView SitexIM")+
    scale_y_continuous(limits =c(0,170000),expand = c(0, 0))+
    expand_limits(x = 0, y = 0)+
    theme(axis.text.x = element_text(size = 10,face="bold"),
          axis.text.y = element_text(size = 13,face= "bold"), 
          panel.background = element_blank(),
          axis.line=element_line(),
          axis.title.x = element_text(size = 8),
          plot.title = element_text(size = 12),
          plot.subtitle  = element_text(size = 12))

```


